Suppl. Figure 2. Differential bacterial abundance across Tissue and Luminal microbiome

### 2023-03-08 reports/manuscript/Suppl.Figure2.Rmd
add figure legend

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.path="./Suppl.Figures/",
  fig.align = "center",
  fig.process = function(filename){
    new_filename <- stringr::str_remove(string = filename, 
                                        pattern = "-1")
    fs::file_move(path = filename, new_path = new_filename)
    ifelse(fs::file_exists(new_filename), new_filename, filename)
})
# setwd("/Users/vilkal/work/Brolidens_work/Projects/broliden_5325/reports/manuscript")
```

@@

```{r Suppl.Fig.2 Diff_bact_abundance, warning=FALSE, message=FALSE, fig.width=10, fig.height=9}
all_microbiome <- cbind(datasets_all_samples[["ASV_Tissue_normalized"]],
                        datasets_all_samples[["ASV_Luminal_normalized"]])
datasets <- factor(c( rep("Tissue",ncol(datasets_all_samples[["ASV_Tissue_normalized"]])) , rep("Luminal",ncol(datasets_all_samples[["ASV_Luminal_normalized"]])) ))
datasets <- datasets[ colSums(all_microbiome)>0 ]
all_microbiome <- all_microbiome[,colSums(all_microbiome)>0]

@@

**Suppl. Figure 2.** Differential bacterial abundance across tissue and CVL microbiome week3 datasets. The results are shown both as **a)** Dot plots and **b)** barplots Bacteria with log2FC above `r fct` and p-value below `r pvt` (from the wilcoxon test) were considered significant and were sorted by the highest expression. The colour scale indicates the difference in total abundance between the datsets as a proportion, where Max is the higest abundace of the two datasets and the other becomes a proportion of this value.The size of the dots indicates the average abundance of the given bacteria in the given dataset.

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.path    = "./Suppl.Figures/",
  fig.align   = "center",
  fig.process = function(filename){
    new_filename <- stringr::str_remove(string = filename, 
                                        pattern = "-1")
    fs::file_move(path = filename, new_path = new_filename)
    ifelse(fs::file_exists(new_filename), new_filename, filename)
})
# setwd("/Users/vilkal/work/Brolidens_work/Projects/broliden_5325/reports/manuscript")
```

@@

### Dot plot and bar plot
```{r Suppl.Fig.2, warning=FALSE, message=FALSE, fig.width=10, fig.height=9}
all_microbiome <- cbind(datasets_all_samples[["ASV_Tissue_normalized"]],
                        datasets_all_samples[["ASV_Luminal_normalized"]])
datasets <- factor(c( rep("Tissue",ncol(datasets_all_samples[["ASV_Tissue_normalized"]])) , rep("Luminal",ncol(datasets_all_samples[["ASV_Luminal_normalized"]])) ))
datasets <- datasets[ colSums(all_microbiome)>0 ]
all_microbiome <- all_microbiome[,colSums(all_microbiome)>0]

@@

**Suppl. Figure 2. Differential bacterial abundance across the luminal and tissue microbiome datasets.** Differential bacterial abundance was compared between the luminal and tissue-adherent microbiome data sets. The results are shown as **a)** dot plots, and **b)** bar plots, respectively. Bacteria with log2FC above `r fct` and p-value `r pvt` (from the Wilcoxon’s test) were considered significantly different and were sorted by the highest expression. The colour scale indicates the difference in total abundance between the datasets as a proportion, where “max” is the highest abundance of the two datasets, and the other becomes a proportion of this value. The size of the dots indicates the average abundance of the given bacteria in the given data set.
